Human capital mediates natural selection in contemporary humans

### 2022-05-04 response-to-reviewers-BE.Rmd

> 7\. The authors write that sigma captures risk aversion in income in their model. But that's confusing and not a good way of describing this for their model, because as far as I understand there's no income risk! They should clarify this and say that sigma regulates the curvature of the utility function, and explain what this means in their riskless model.

It is a fair point. We have rewritten accordingly: "$\sigma > 0$ measures the curvature of the utility function, i.e. the decline in marginal utility of income as income increases".\

> OTHER COMMENTS AND SUGGESTIONS
>
> 8\. Most figures are hard to read. For example, Figures 3-5 are hard to read. In Figure 3a, the dot color indicate education and the dot border color indicates significance; that's very difficult to read quickly (for instance, a blue dot with a yellow border looks green). Instead, the authors could use different symbols (crosses, squares) for education and colors for significance, or vice-versa.

We have changed our figures to use both shape and colour for categories. We hope this is an improvement. We've also worked on Figure 1.

### 2022-05-04 why-natural-selection.Rmd
More text tweaks. No need for picture in response to reviewers.

```{r plot-means-over-time, fig.height = 7, fig.cap = "Mean polygenic scores (PGS) by birth year in UK Biobank. Circles are means for 5-year intervals. Lines are 95% confidence intervals. Triangles show a significant linear increase or decrease over time (p < 0.05/33)."}

@@

We also examine selection effects among respondents' parents, using information
on respondents' number of siblings to calculate parents' RLRS. Effect sizes of
polygenic scores are highly correlated across the two generations (Appendix
Figure \@ref(fig:plot-res-sibs)). Median-splitting respondents by year of birth,
we find little evidence of change in effect sizes among the parents' generation.
There is some evidence that selection effect sizes are increasing in the 
respondents' generation, with 9 polygenic scores showing a significant increase. 
We also check whether selection effects vary by
AFLB and socio-economic status in the parents' generation, using the 1971 
Townsend deprivation score of respondents' birthplace as a proxy for income
[@townsend1987deprivation]. Results show the same pattern as for the
respondents' generation. Effect sizes are larger and more often significant in
the most deprived areas (Appendix Figure \@ref(fig:plot-siblings-townsend)).
Effects are larger among younger fathers and mothers, and change sign when
controlling for AFLB (Appendix Figures \@ref(fig:plot-age-birth-parents-cross),
\@ref(fig:plot-age-birth-parents)). Lastly, we check for a "quantity-quality
tradeoff" between parents' number of children and number of grandchildren. We
don't find any: in fact, the correlation between respondents' and parents' RLRS
is positive ($\rho$ = `r sib_chn_cor$estimate`, $p < 2 \times 10^{-16}$).

>>>>

```{r plot-means-over-time, fig.height = 7, fig.cap = "Mean polygenic scores (PGS) by birth year in UK Biobank. Symbols show means for 5-year intervals. Bars are 95% confidence intervals. Triangles denote a significant linear increase or decrease over time (p < 0.05/33)."}

@@

We also examine selection effects among respondents' parents, using information
on respondents' number of siblings to calculate parents' RLRS. Effect sizes of
polygenic scores are highly correlated across the two generations (Appendix
Figure \@ref(fig:plot-res-sibs)). Median-splitting respondents by year of birth,
we find little evidence of change in effect sizes among the parents' generation.
There is some evidence that selection effect sizes are increasing in the 
respondents' generation, with 8 polygenic scores showing a significant increase. 
We also check whether selection effects vary by
AFLB and socio-economic status in the parents' generation, using the 1971 
Townsend deprivation score of respondents' birthplace as a proxy for income
[@townsend1987deprivation]. Results show the same pattern as for the
respondents' generation. Effect sizes are larger and more often significant in
the most deprived areas (Appendix Figure \@ref(fig:plot-siblings-townsend)).
Effects are larger among younger fathers and mothers, and change sign when
controlling for AFLB (Appendix Figures \@ref(fig:plot-age-birth-parents-cross),
\@ref(fig:plot-age-birth-parents)). Lastly, we check for a "quantity-quality
tradeoff" between parents' number of children and number of grandchildren. We
don't find any: in fact, the correlation between respondents' and parents' RLRS
is positive ($\rho$ = `r sib_chn_cor$estimate`, $p < 2 \times 10^{-16}$).
